BurgerTown Presents: Open Adcess

### 2017-04-27 paper-sponsorships.tex
bqhatevwr

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
\caption{Have you seen this boy?}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/ad.jpg}
\caption{Have you seen this boy? He's a great catch! He's not very bright, and he has your brother's thighs, those Goodman thighs. He's no Clark Gable either, but he's \checkmark tall \checkmark detoxing from that juice craze, oh such a thrill that was \checkmark the doctors ask does he have sensory interests others find unusual, I say I don't know but he's probably \checkmark better with these checklists than I am \checkmark almost certainly willing to testify as an alibi, no questions asked. That's a rare attribute, especially these days. That boy, I worry, though, I worry. He doesn't eat. But he's got no one, it kills me. You know, the Ablemans, they have grandkids thanks to this Internet. I hope if I send this to these computer science people, they put it on the Internet and make the shidduch.}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/cambridge.jpg}
\caption{Visit beautiful Cambridge, MA. ``Where class privilege goes to reproduce itself.''}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.45\textwidth]{figures/lowell.jpg}
\caption{Visit Lowell, MA. ``Where}
\end{figure}
